
\begin{description}
  \item[2022/12/30] -- added info about Nameref issues with \cmd{caption} to the section \nameref{faq:packages}.
  \item[2022/11/28] -- added example for restoring commands using \verb|\RestoreMathJaxEnvironments| in the \nameref{sec:howto-mathjax} section.
  \item[2022/11/25] -- added example for handling of multiple indices to the \nameref{sec:indexing} how-to.
  \item[2022/10/23] -- added info about the \option{Gin-percent} option.
  \item[2022/10/21] -- finished the \nameref{sec:howto-mathjax} section.
  \item[2022/10/20] -- added \nameref{sec:howto-mathml} how-to.
  \item[2022/10/18] -- added \nameref{sec:howto-picm} how-to.
  \item[2022/10/17] -- added how-to for bibliography and moved most of the content of MathJax configurations to a new how-to section on MathJax. 
  \item[2022/10/17] -- use \verb|\Configure{MathJaxSource}| instead of \verb|\Configure{MathjaxSource}|.
  \item[2022/09/22] -- added links to mailing list and issue tracker in the Troubleshooting section.
  \item[2022/09/22] -- added information about the \texttt{--mode clean} option to the Troubleshooting section.
  \item[2022/09/21] -- added section about early package fixes with \file{<pkgname>-hooks.4ht} files and \file{usepackage.4ht} to the chapter \nameref{sec:developers}.
  \item[2022/08/17] -- fixed external CSS example.
  \item[2022/06/16] -- added the \nameref{sec:indexing} howto.
  \item[2022/06/14] -- added info about \cmd{Tag} and related cross-referencing commands.
  \item[2022/06/08] -- added info about \cmd{hbox} issue with MathML to FAQ.
  \item[2022/05/18] -- added section on custom output formats.
  \item[2022/05/17] -- added tutorial and other fixes to the for developers chapter.
  \item[2022/05/13] -- the \cmd{cmd} command is now robust. Added info about the \option{cut-fullname} option.
  \item[2022/05/02] -- added example of bracket balancing for MathJax.
  \item[2022/04/27] -- updated numerical options for section cutting. Added examples for \cmd{PauseCutAt}.
  \item[2022/04/18] -- added example of \makefourht{} build file.
  \item[2022/04/12] -- added TOC and sectioning sections.
  \item[2022/04/11] -- added page breaks sections.
  \item[2022/04/10] -- updated sections about math and pictures in the Configurations chapter.
  \item[2022/04/08] -- subsection about \makefourht{} extensions in Calling Commands chapter.
  \item[2022/04/06] -- added info about paragraph handling commands, rewrote logical blocks section.
  \item[2022/04/05] -- added info about supported engines in the Calling Commands chapter. Added ODT options.
  \item[2022/04/04] -- updated chapter Calling Commands.
  \item[2022/04/01] -- fixed issues with unwanted ligatues in inline code commands.
  \item[2022/03/27] -- info about TITLE+ configuration.
  \item[2022/03/25] -- added documentation for the \cmd{Configure} command, examples for CSS.
  \item[2022/03/24] -- added Rmarkdown example.
  \item[2022/03/23] -- updated FAQ, added options section to tutorial.
  \item[2022/03/22] -- added supported output formats, updated \fourhtsty\ options instructions, continuing in tutorial rewrite.
  \item[2022/03/21] -- added link to example of \href{https://tex.stackexchange.com/a/637910/2891}{MathML code with \LaTeX\ annotations}.
  \item[2022/03/18] -- added \texcommand{\namerefpage} command. It prints crosslink title and in the PDF mode also page number.
  \item[2022/03/17] -- updated tutorial to use custom code environments, removed some obsolete information.
  \item[2022/01/26] -- added description for options that break HTML pages to subpages based on sectioning level.
  \item[2022/01/12] -- updated information about alternative text in Graphics HowTo.
  \item[2021/10/25] -- added example how to handle custom environments in MathJax output -- \nameref{sec:mathjax_env}.
  \item[2021/06/29] -- updated introduction to \nameref{sec:private-configuration}.
  \item[2021/06/13] -- added information  about \nameref{faq:compilation_errors} (\ref{faq:compilation_errors}) and \nameref{faq:dom_processing} (\ref{faq:dom_processing}).
  \item[2021/06/13] -- started tracking of changes.
\end{description}
